\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}

\geometry{margin=1in}
\pagestyle{fancy}
\fancyhf{}
\rhead{ID: VAB-02012026-1.060-MASTER}
\lhead{Berard Trust: Sovereign Record}
\cfoot{\thepage}

\title{\textbf{The Berard Group of Mathematics:}\\ \large A Unified Theory of Informational Rigidity}
\author{Vernon Arthur Berard (The Architect) \\ \small Sole Custodian, Berard Trust}
\date{February 1, 2026}

\begin{document}

\maketitle

\begin{abstract}
This document formalizes the Einstein-Berard Law and the operational calculus of the Berard Group. It introduces Manifold Stiffness ($S_0$) and the 0.10 Hz Global Master Interrupt ($B$) as the fundamental regulators of the vacuum, resolving gravitational singularities into Finite Density Cores and providing a non-singular cosmological "Bounce" model.
\end{abstract}

\section{The Core Axioms: The Einstein-Berard Law}
The fundamental extension of mass-energy equivalence is defined by the governing equation:

\begin{equation}
E = (mc^2) \cdot (BC^2) \cdot \left(\frac{1}{S_0^2}\right)
\end{equation}

Where:
\begin{itemize}
    \item $m$: Relativistic Mass.
    \item $c$: Velocity of Light.
    \item $B$: The Berard Constant (0.10 Hz), acting as the Global Master Interrupt.
    \item $S_0$: Manifold Stiffness, representing the vacuum's resistance to information loss.
\end{itemize}

\section{The Calculus: Generator and Lagrangian}
The Berard Group is a Dilation Symmetry Group driven by the scaling operator:

\begin{equation}
\mathcal{D}_B = -i \left( S \frac{\partial}{\partial S} \right)
\end{equation}

The non-zero commutator $[\hat{H}, \mathcal{D}_B] \neq 0$ necessitates the cosmic pulse at 0.10 Hz to purge variance. The resulting flow of entropy is described by the Berard Current (The Tensor Muffler):

\begin{equation}
J^\mu_B = T^{\mu\nu} x_\nu + \lambda S_0 \partial^\mu S_0
\end{equation}

\section{Geometry and Metric Solutions}
Spacetime curvature is modulated by Stiffness Screening $\Phi_B(r) = (S_{vac} / S_0(r))^2$, leading to the Berard Metric:

\begin{equation}
ds^2 = - \left( 1 - \frac{2GM}{r c^2} \Phi_B(r) \right) c^2 dt^2 + \dots
\end{equation}

As $r \to 0$, $S_0$ rises to infinity, canceling gravitational divergence and replacing singularities with a Finite Density Core.

\section{Legal Mandate}
All Rights Reserved 2026. This document and the theories contained herein are the exclusive property of the \textbf{Berard Trust}. Any utilization is subject to the \textit{Berard Trust Charter Mandate}.

\end{document}